Emissions and Perceptions of Climate Change

### 2022-12-06 Code/Drafts/Final_Short_Oral_Presentation.Rmd
Trying Diverging graphs and new chi squared method

---
title: "Emissions and Perceptions of Climate Change"
author: "Rae Dunbar"
date: "11/13/2022"
output:
  html_document: default
  pdf_document: default
---

@@

@@

>>>>

---
title: "Emissions and Perceptions of Climate Change"
author: "Rae Dunbar"
date: "11/13/2022"
output:
  pdf_document: default
  html_document: default
---

@@

```{r}
library(scales)
fuels<- fuels %>% mutate(percent=paste0(round(Number, digits=1), "%"))
ggplot(fuels, aes(x=Country, y=Number, fill=response)) + 
  geom_col()+ #also makes a bar graph
  geom_text(aes(label=percent), position=position_stack(vjust = 0.5), color="white", fontface="bold")+ #stack stacks them, fontface bolds  the numbers in the bargraphs 
  coord_flip()+
  scale_x_discrete()+
  scale_fill_viridis_d()+
  labs(title="How much Fossil Fuels Should We Use", x=NULL, fill=NULL)

```
```{r}
fuels_diverging <- fuels %>% mutate(percent=if_else(response %in% c("Much less", "Somewhat less"), Number, -Number)) 
#everything in there 
```

```{r}
fuels_diverging<- fuels_diverging %>% mutate(percent=paste0(round(percent, digits=1), "%"))
ggplot(fuels_diverging, aes(x=Country, y=Number, fill=response)) + 
  geom_col()+ #also makes a bar graph
  geom_text(aes(label=percent), position=position_stack(vjust = 0.5), color="white", fontface="bold")+ #stack stacks them, fontface bolds  the numbers in the bargraphs 
  coord_flip()+
  scale_x_discrete()+
  scale_fill_viridis_d()+
  labs(title="How much Fossil Fuels Should We Use", x=NULL, fill=NULL)+
 theme_minimal()+
  theme(axis.text.x=element_blank(), axis.title.x=element_blank(),
panel.grid=element_blank(),
legend.position="top")
```

@@

```{r}
ugh<- survey %>% filter()
```

```{r}
fuels_numPeople<-fuels_numPeople %>% filter(response != "Don't know") #excluding don't know

fuels_numPeople$grouped_answer<- NA
more<- which( fuels_numPeople$response== "Much less" |fuels_numPeople$response== "Somewhat less" )
less<- which( fuels_numPeople$response== "Much more" |fuels_numPeople$response== "Somewhat more" | fuels_numPeople$response== "Refused" |fuels_numPeople$response== "Same amount as today")

  fuels_numPeople$grouped_answer[more]<- "more"
  fuels_numPeople$grouped_answer[less]<- "less"

fuels_numPeople<- fuels_numPeople %>% group_by(Country, grouped_answer) %>% summarise(grouped_number=sum(total))

fuels_numPeople<- fuels_numPeople %>% filter(grouped_answer != is.na)
```
